Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-30 paper.tex
Updated References
Work in progress. Still missing previous work.

    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
    life-cycle of animal species. As in nature, population individuals grow older % \cite{Felix-Saul2022}
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    We previously used to generate a new random % In a previous work (reference) - M
    set of solutions, with the cost of losing all evolution knowledge.

@@

    In previous work, we presented an algorithm inspired by nature, where we % Reference
    model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

\bibliographystyle{splncs03_unsrt}
%\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}

@@

% TO-DO: Turniting.

>>>>

    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
    and age. In this algorithm's reproduction process, couples must match by mutual
    attraction, where sometimes individuals won't procreate offspring because of
    the mate's low appeal. As time passes, the environment kills its individuals
    either because of low fitness or age, causing occasional population extinction.
    % Just to be sure explain a bit more what we mean by extinsion. - M
    When this condition presents itself, it is required to create a new population
    to continue evolution (restart). 
    % Maybe you do it later, but explain what is a restart precisely 
    We previously used to generate a new random % In a previous work (reference) - M
    set of solutions, with the cost of losing all evolution knowledge.

@@

    In previous work, we presented an algorithm inspired by nature 
    \cite{Felix-Saul2022}, where we model our algorithm based on
    the generalization of the life cycle of animal species. Our algorithm, as
    in nature, consists of four stages \cite{read1968system}: birth, growth,
    reproduction, and death. One key concept of our idea is that combining
    those processes evolves the population. We propose to execute all these
    stages in parallel and asynchronously on a continuously evolving
    population.

@@

\bibliographystyle{splncs03_unsrt}
%\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}
%\bibliography{10.1007_978-3-031-08266-5_8-citation.bib}

@@

% TO-DO: Turnitin.
